Behavior Driven Development in Haskell

### 2012-06-02 paper.tex
Grammar
Wording

Haddock has markup support for code blocks, and code blocks are widely used
to include properties and examples into documentation\footnote{
See e.g. the documentation of
{\tt containers},
{\tt filepath},
{\tt bytestring} or
{\tt text}}.
Here is an example from the {\tt filepath} package.

@@

\noindent The {\tt it} function combines a text description for a
behavior and some evidence (a code example or a property) into a spec.
Code examples can be arbitrary HUnit assertions.  Properties must be of type {\tt
Property}; QuickCheck's \texttt{property} function can be used to turn
arbitrary properties into a \texttt{Property}.

>>>>

Haddock has markup support for code blocks, and code blocks are widely used
to include properties and examples into documentation\footnote{
See e.g. the documentation of
{\tt containers},
{\tt filepath},
{\tt bytestring} or
{\tt text}.}.
Here is an example from the {\tt filepath} package.

@@

\noindent The {\tt it} function combines a text description for a
behavior and some evidence (a code example or a property) into a spec.
Code examples can be arbitrary HUnit test cases\footnote{%
Wrapping the test case with HUnit's {\tt TestCase} constructor is not
necessary.}.  Properties must be of type {\tt
Property}.  QuickCheck's \texttt{property} function can be used to turn
an arbitrary properties into values of type \texttt{Property}.
